Effects of resonant and random excitations on the proton beam in the Large Hadron Collider, with applications to the design of a pulsed hollow electron lens for active halo control

### 2018-03-23 resex.tex
Minor changes to bibliography.
Revisions in title and abstract

\usepackage{bm}
\usepackage{dcolumn}
\usepackage{graphicx}
\usepackage[colorlinks=true, linkcolor=blue, citecolor=blue,
            filecolor=blue, urlcolor=blue]{hyperref}

@@

\title{Experimental and numerical studies of the effects of resonant
  and random excitations of the proton beam in the LHC, with
  applications to the design of a pulsed hollow electron lens for
  active halo control}

@@

\begin{abstract}
  In the High Luminosity Large Hadron Collider (HL-LHC), a
  considerable amount of energy will be stored in the beam tails, due
  to the high beam intensity and to an overpopulation of the tails
  compared to a Gaussian distribution. To control and clean the beam
  halo, the installation of two hollow electron lenses (HEL), one per
  beam, is being considered. In standard electron-lens operation, a
  proton bunch sees the same electron current at every
  revolution. Pulsed operation (i.e., different current for different
  turns) is also considered, because it can widen the range of
  achievable halo removal rates. For an axially symmetric electron
  lens, only the halo particles are excited, leaving the core
  unperturbed. If a residual field is present at the location of the
  beam core, these particles are exposed to transverse kicks and to
  noise. In this paper, we present the results of numerical
  simulations and of the LHC experiments conducted in~2016 and~2017 to
  study the effects of random noise and of resonant excitations on the
  beam core. The excitation patterns were generated by the transverse
  damper system, which is a very flexible source of transverse dipole
  kicks. The main observables were losses, emittances, and transverse
  distributions as a function of excitation patterns and
  strengths. The resonant excitations showed rich nonlinear dynamics
  and nontrivial changes of the beam distribution, which, to our
  knowledge, have not previously been observed and studied in this
  detail. We also give estimates, based upon existing measurements of
  prototype electron guns, of the residual fields that may be expected
  in the HL-LHC hollow electron lens.
\end{abstract}

>>>>

\usepackage{bm}
\usepackage{dcolumn}
\usepackage{graphicx}
\usepackage[dvipsnames]{xcolor}
\usepackage[colorlinks=true, allcolors=NavyBlue]{hyperref}

@@

\title{Effects of resonant and random excitations on the proton beam
  in the Large Hadron Collider, with applications to the design of a
  pulsed hollow electron lens for active halo control}

@@

\begin{abstract}
  We present the results of numerical simulations and experimental
  studies about the effects of random and resonant excitations on
  proton losses, emittances, and beam distributions in the Large
  Hadron Collider (LHC). In addition to shedding light on complex
  nonlinear effects, these studies are applied to the design of hollow
  electron lenses (HEL) for active beam halo control. In the
  High-Luminosity Large Hadron Collider (HL-LHC), a considerable
  amount of energy will be stored in the beam tails. To control and
  clean the beam halo, the installation of two hollow electron lenses,
  one per beam, is being considered. In standard electron-lens
  operation, a proton bunch sees the same electron current at every
  revolution. Pulsed electron beam operation (i.e., different currents
  for different turns) is also considered, because it can widen the
  range of achievable halo removal rates. For an axially symmetric
  electron beam, only protons in the halo are excited. If a residual
  field is present at the location of the beam core, these particles
  are exposed to time-dependent transverse kicks and to noise. We
  discuss the numerical simulations and the experiments conducted
  in~2016 and~2017 at injection energy in the LHC. The excitation
  patterns were generated by the transverse feedback and damping
  system, which acted as a very flexible source of dipole kicks. The
  main observables were losses, emittances, and transverse
  distributions as a function of excitation patterns and
  strengths. The resonant excitations induced rich dynamical effects
  and nontrivial changes of the beam distributions, which, to our
  knowledge, have not previously been observed and studied in this
  detail. We conclude with a discussion of the tolerable and
  achievable residual fields and proposals for further studies.
\end{abstract}
